### 2014-07-31 paper/paper.tex
Sent a draft to Fei Song. Hopefully this will go ok

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c|c|r|r|r|r|}
        \hline
        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
        \hline
        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. Sorted by
        average F-score.}
    \label{table:results}
\end{table}

@@

I am great and without reproach.

>>>>

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
        \hline
          & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
                    \hline
        a & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
        b & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
        c & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
        d & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
        e & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
        f & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
        g & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
        h & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
        i & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
        j & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
        k & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
        l & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
        m & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
        n & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
        o & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
        p & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training.}
    \label{table:results}
\end{table}

%TODO write about the number of features

@@

\textit{Note: I would like to finish the results section before I start this section }
